~\\ \Large\bf Data Intensive processing with iRODS and the middleware CiGri for the Whisper project

### 2014-09-01 articles/2014/whisper/aricleEbauche/Draft_BriandBzeznikIrodsUserMeeting2014.tex
Added figures references

Each cluster of the University of Grenoble uses the resource manager OAR. CiGri acts, among other things, as a metascheduler of OAR.
It retrieves the clusters states trough OAR and submits the jobs on free resources without exhausting the local scheduling queues.

\begin{center}%[h]
\centering
\captionof{figure}{\label{schemaCigriArch} Cigri communications}
\includegraphics[width=8cm]{cigri_arch.png}
\end{center}

@@

Roughly speaking, in order to run a campaign, the user describes through a file (in the JSON format) the parameters of the campaign 
such as the accepted cluters, the needed resources, the maximum duration, the location of the codes, a prologue or epilogue script,...  
Codes and input data are retrieved from iRODS using i-commands into the prologue scripts and the jobs scripts (or using the iRODS API if the jobs are written into a supported language). So, there's no direct connexion between CiGri and iRODS, but the usage is totally complementary through the jobs scripts. 
Moreover, the user defines also a file where each line represents a value of the parameter for the user's code.
Thus, the number of line of these parameter file corresponds to the number of jobs of the campaign.

\begin{center}%[h]
\centering
\captionof{figure}{\label{schemaCigriJDL} Cigri jobs campaign submission}
\includegraphics[width=8cm]{cigri_sub.png}
\end{center}

>>>>

Each cluster of the University of Grenoble uses the resource manager OAR. CiGri acts, among other things, as a metascheduler of OAR.
It retrieves the clusters states trough the OAR RESTful API (figure \ref{schemaCigriArch}) and submits the jobs on free resources without exhausting the local scheduling queues.

\begin{center}%[h]
\centering
\captionof{figure}{\label{schemaCigriArch} Cigri communications}
\includegraphics[width=6cm]{cigri_arch.png}
\end{center}

@@

\begin{center}%[h]
\centering
\captionof{figure}{\label{schemaCigriJDL} Cigri jobs campaign submission}
\includegraphics[width=7cm]{cigri_sub.png}
\end{center}

Roughly speaking, in order to run a campaign, the user describes through a file (in the JSON format) the parameters of the campaign 
such as the accepted cluters, the needed resources, the maximum duration, the location of the codes, a prologue or epilogue script,...  
Codes and input data are retrieved from iRODS using i-commands into the prologue scripts and the jobs scripts (or using the iRODS API if the jobs are written into a supported language). So, there's no direct connexion between CiGri and iRODS, but the usage is totally complementary through the jobs scripts. 
Moreover, the user defines also a file where each line represents a value of the parameter for the user's code.
Thus, the number of line of these parameter file corresponds to the number of jobs of the campaign (figure \ref{schemaCigriJDL}).
